---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
library(CPreval)
```

[![Travis-CI Build Status](https://travis-ci.org/SMAC-Group/simts.svg?branch=master)](https://travis-ci.org/SMAC-Group/simts)
[![Licence](https://img.shields.io/badge/licence-AGPL--3.0-blue.svg)](https://opensource.org/licenses/AGPL-3.0)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-6666ff.svg)](https://cran.r-project.org/)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-green.svg)](https://github.com/SMAC-Group/simts)

# `CPrval` Overview 

This R package provides an implementation of the estimators discussed in *Accurate Prevalence Estimation for Emerging or Rare Infectious Diseases* by Stéphane Guerrier, Christoph Kuzmics and Maria-Pia Victoria-Feser (submitted manuscript available upon request). The pacakge can be installed from GitHub as follows:

```{r, eval=FALSE}
# Install devtools
install.packages("devtools")

# Install the package from GitHub
devtools::install_github("stephaneguerrier/CPreval")
```

## Example

Consider the following data:

```{r}
seed = 18
n    = 1500
p0   = 3/100
pi0  = 1/100
(X = sim_Rs(p = p0, pi0 = pi0, n = n, seed = seed))
```

Estimators:

```{r}
survey_sample(X$R, X$n)
moment_estimator(R0 = X$R0, R = X$R, pi0 = X$pi0, n = X$n)
mle(R0 = X$R0, R = X$R, pi0 = X$pi0, n = X$n)
```

With measurement error:

```{r}
alpha0 = 1/100
alpha  = 1/100
beta0  = 6/100
beta   = 6/100
(X = sim_Rs(p = p0, pi0 = pi0, n = n, seed = seed,
           alpha = alpha, alpha0 = alpha0, 
           beta = beta, beta0 = beta0))
```

Without taking into account measurement error:

```{r}
survey_sample(X$R, X$n)
moment_estimator(R0 = X$R0, R = X$R, pi0 = X$pi0, n = X$n)
mle(R0 = X$R0, R = X$R, pi0 = X$pi0, n = X$n)
```

Taking into account measurement error:

```{r}
survey_sample(X$R, X$n, alpha = alpha, beta = beta)
moment_estimator(R0 = X$R0, R = X$R, pi0 = X$pi0, n = X$n, 
                 alpha = alpha, alpha0 = alpha0, 
                 beta = beta, beta0 = beta0)
mle(R0 = X$R0, R = X$R, pi0 = X$pi0, n = X$n, 
                 alpha = alpha, alpha0 = alpha0, 
                 beta = beta, beta0 = beta0)
```

## License

The license this source code is released under is the GNU AFFERO GENERAL PUBLIC LICENSE (AGPL) v3.0. Please see the LICENSE file for full text. Otherwise, please consult [TLDR Legal](https://tldrlegal.com/license/gnu-affero-general-public-license-v3-(agpl-3.0)) or [GNU](https://www.gnu.org/licenses/agpl-3.0.en.html) which will provide a synopsis of the restrictions placed upon the code.
