---
title: "Simulation Study"
bibliography: biblio.bib
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{Simulations Study}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(knitr)
library(kableExtra)
```

In this simulation study, we compare the performance of the three estimators considered in @guerrier2020accurate, namely the sample survey, $\bar{\pi}$, the MLE $\hat{\pi}$ as well as the moment estimator $\tilde{\pi}$. All simulation results are based on $B = 10^4$ Monte-Carlo replications and we consider 24 simulation settings, which are presented in the table below:

```{r setting, fig.align='center'}
# Load package
library(CPreval)

# Number of Monte-Carlo simulations 
B = 10^4

# Initial simulation seed
seed = 1832  

# Simulation settings
simu = data.frame(Simulation = 1:24,
                  p0 = 100*rep(c(2/1000, 20/1000, 150/1000, 500/1000), 6),
                  pi0 = 100*rep(c(1/1000, 10/1000, 100/1000, 300/1000), 6),
                  n = rep(c(rep(1500, 4), rep(15000, 4)), 3),
                  alpha = 100*c(rep(0, 8), rep(0, 8), rep(0.01,8)),
                  beta = 100*c(rep(0, 8), rep(0.02,8), rep(0.02,8)))
 
# Print table
kable(simu, col.names = c("Simulation ID",
                           "$p_0$ (%)",
                           "$\\pi_0$ (%)",
                           "Sample size $n$",
                           "$\\alpha_0 = \\alpha$ (%)",
                           "$\\beta_0 = \\beta$ (%)")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

The code below performs the simulation:

```{r simu, cache = TRUE}
# Initialisation       
error_survey = error_moment = error_mle = matrix(NA, B, 24)  
boundary_survey = boundary_mle = boundary_moment = matrix(NA, B, 24)  
length_survey = length_mle = matrix(NA, B, 24)  
coverage_survey =  coverage_mle  = matrix(NA, B, 24)  

# Start Monte-Carlo   
for (j in 1:24){
  for (i in 1:B){
    # Simulate data
    X = sim_Rs(p = simu$p0[j]/100, pi0 = simu$pi0[j]/100, n = simu$n[j], seed = seed + i,
               alpha0 = simu$alpha[j]/100, alpha = simu$alpha[j]/100,
               beta0 = simu$beta[j]/100, beta = simu$beta[j]/100)
    
    # Fit survey sample estimator
    survey = survey_sample(R = X$R, n = X$n, alpha = X$alpha, beta = X$beta, pi0 = X$pi0, simulation = TRUE)
    
    # Estimation error
    error_survey[i,j] = survey$estimate - simu$p0[j]/100
    
    # Check boundary 
    boundary_survey[i,j] = survey$boundary
  
    # Length of CI
    length_survey[i,j] = survey$ci_cp[2] - survey$ci_cp[1]
    
    # Coverage
    coverage_survey[i,j] = survey$ci_cp[1] < simu$p0[j]/100 && survey$ci_cp[2] > simu$p0[j]/100
    
    # Moment estimator
    moment = moment_estimator(R0 = X$R0, R = X$R, pi0 = X$pi0, n = X$n, alpha0 = X$alpha0, 
                              alpha = X$alpha, beta0 = X$beta0, beta = X$beta, simulation = TRUE)
  
    # Estimation error
    error_moment[i,j] = moment$estimate - simu$p0[j]/100
    
    # Boundary 
    boundary_moment[i,j] = moment$boundary
   
    # MLE
    ml = mle(R0 = X$R0, R = X$R, pi0 = X$pi0, n = X$n, alpha0 = X$alpha0, 
              alpha = X$alpha, beta0 = X$beta0, beta = X$beta, simulation = TRUE)
    
    # Estimation error
    error_mle[i,j] = ml$estimate - simu$p0[j]/100
    
    # Boundary 
    boundary_mle[i,j] = ml$boundary
    
    # Length of CI
    length_mle[i,j] = ml$ci_cp[2] - ml$ci_cp[1]
    
    # Coverage
    coverage_mle[i,j] = ml$ci_cp[1] < simu$p0[j]/100 && ml$ci_cp[2] > simu$p0[j]/100
  } 
}
```

The table below presents the percentage of times each estimator had a solution either outside of the interval $[\pi_0, 1]$ (moment estimator) or at its boundary (MLE and sample survey):

```{r}
# Simulation settings
boundary = data.frame(Simulation = 1:24,
                  survey = apply(boundary_survey, 2, mean),
                  moment = apply(boundary_moment, 2, mean),
                  mle = apply(boundary_mle, 2, mean))
 
# Print table
kable(boundary, col.names = c("Simulation ID",
                           "Survey sample $\\bar{\\pi}$",
                           "Moment Estimator $\\tilde{\\pi}$",
                           "MLE $\\hat{\\pi}$")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

The same information is presented as a barplot in the figure below:

```{r, fig.align='center', fig.width=10, fig.height=6}
boundary_barplot = 100*t(as.matrix(boundary[,2:4]))
colnames(boundary_barplot) = boundary[,1]
cols = hcl(h = seq(15, 375, length = 4), l = 65, c = 100)[1:3]
barplot(boundary_barplot, beside = TRUE, col = cols[c(1,3,2)], 
        ylab = "Percentage of simulations with no reliable solution",
        xlab = "Simulation ID")
legend("topleft", c("Survey", "Moment", "MLE"), fill = cols[c(1,3,2)], bty = "n")
```

In the figure below we compare the ratio of the RMSEs:

```{r, fig.align='center', fig.width=10, fig.height=6}
RMSE = function(x)
  sqrt(mean(x)^2 + var(x))

nb_settings = tail(simu$Simulation, n=1)
cols = hcl(h = seq(15, 375, length = 4), l = 65, c = 100)[1:3]

rmse_survey = apply(error_survey, 2, RMSE)
rmse_moment = apply(error_moment, 2, RMSE)
rmse_mle = apply(error_mle, 2, RMSE)

plot(NA, xlim = c(1,nb_settings), ylim = c(0.2, 1.15), xlab = "Simulation ID", 
     ylab = "Ratio of RMSE", axes = FALSE)
rect(0.5, -0.01, 4.5, 1, col = "grey95", border = "grey95")
rect(8.5, -0.01, 12.5, 1, col = "grey95", border = "grey95")
rect(16.5, -0.01, 20.5, 1, col = "grey95", border = "grey95")
text(2.5, 0.25, "n = 1,500")
text(6.5, 0.25, "n = 15,000")
text(10.5, 0.25, "n = 1,500")
text(14.5, 0.25, "n = 15,000")
text(18.5, 0.25, "n = 1,500")
text(22.5, 0.25, "n = 15,000")
text(4.5, 1.1, "without measurement error")
text(12.5, 1.1, "with false positive")
text(20.5, 1.1, "with false positive and negative")
abline(v = 8.5, lwd = 2, lty = 2)
abline(v = 16.5, lwd = 2, lty = 2)
axis(1, 1:nb_settings)
axis(2)
grid()
abline(v = 1:nb_settings, col = "grey80", lty = 3)
abline(h = (0:20)/10, col = "grey80", lty = 3)
box()
abline(h = 1, lwd = 2)
lines(1:nb_settings, rmse_mle/rmse_survey, col = cols[1], pch = 15, type = "b")
lines(1:nb_settings, rmse_mle/rmse_moment, col = cols[3], pch = 16, type = "b")
abline(h = 1, lwd = 2)
legend(1, 0.45, c("Survey Sample", "Moment Estimator"), col = cols[c(1,3)],
       pch = c(15, 16), lwd = 1, bty = "n")
```

```{r, fig.width=10, fig.height=10}
par(mfrow = c(2,1), mar = c(0.5,0.5,0.5,0.5), oma = c(5,5,3,0))

# Compute empirical coverage
cov_survey = 100*apply(coverage_survey, 2, mean)
cov_mle = 100*apply(coverage_mle, 2, mean)

# Compute average length of CI
len_survey = apply(length_survey, 2, mean)
len_mle = apply(length_mle, 2, mean)

# Plot coverage
plot(NA, xlim = c(1,nb_settings), ylim = c(93.5, 100.8), xlab = " ", ylab = " ", axes = FALSE)
rect(0.5, 0, 4.5, 150, col = "grey95", border = "grey95")
rect(8.5, 0, 12.5, 150, col = "grey95", border = "grey95")
rect(16.5, 0, 20.5, 150, col = "grey95", border = "grey95")
text(2.5, 94, "n = 1,500")
text(6.5, 94, "n = 15,000")
text(10.5, 94, "n = 1,500")
text(14.5, 94, "n = 15,000")
text(18.5, 94, "n = 1,500")
text(22.5, 94, "n = 15,000")
text(4.5, 100.5, "without measurement error")
text(12.5, 100.5, "with false positive")
text(20.5, 100.5, "with false positive and negative")
abline(v = 8.5, lwd = 2, lty = 2)
abline(v = 16.5, lwd = 2, lty = 2)
axis(2)
grid()
abline(v = 1:nb_settings, col = "grey80", lty = 3)
abline(h = 90 + (0:10), col = "grey80", lty = 3)
box()
abline(h = 95, lwd = 2)
mtext("Empirical coverage (95% conf. level)", side = 2, line = 3)
lines(cov_survey, col = cols[1], pch = 16, type = "b")
lines(cov_mle, col = cols[2], pch = 17, type = "b")

legend(2.5, 99.5, c("Survey Sample", "MLE"), col = cols[c(1,2)],
       pch = c(15, 17), lwd = 1, bty = "n")


plot(NA, xlim = c(1,nb_settings), ylim = c(0.595, 1.02), xlab = " ", ylab = " ", axes = FALSE)
rect(0.5, 0, 4.5, 1.50, col = "grey95", border = "grey95")
rect(8.5, 0, 12.5, 1.50, col = "grey95", border = "grey95")
rect(16.5, 0, 20.5, 1.50, col = "grey95", border = "grey95")
text(2.5, 0.59, "n = 1,500")
text(6.5, 0.59, "n = 15,000")
text(10.5, 0.59, "n = 1,500")
text(14.5, 0.59, "n = 15,000")
text(18.5, 0.59, "n = 1,500")
text(22.5, 0.59, "n = 15,000")
text(4.5, 1.01, "without measurement error")
text(12.5, 1.01, "with false positive")
text(20.5, 1.01, "with false positive and negative")
abline(v = 8.5, lwd = 2, lty = 2)
abline(v = 16.5, lwd = 2, lty = 2)
axis(2)
axis(1, at = 1:24)
grid()
abline(v = 1:nb_settings, col = "grey80", lty = 3)
abline(h = (0:10)/10, col = "grey80", lty = 3)
box()
mtext("Ratio of average length of 95% CI", side = 2, line = 3)
mtext("Simulation ID", side = 1, line = 2)
abline(h = 1, lwd = 2)
cols2 = hcl(h = seq(15, 375, length = 5), l = 65, c = 100)[1:4]
lines(len_mle/len_survey, type = "b", ylim = c(0.6, 1.01),
      col = cols2[4], pch = 18, cex = 1.4)
```

# References
